\chapter*{Abstract\markboth{Abstract}{}}
\addcontentsline{toc}{chapter}{Abstract}

This is the project documentation of a group from the course of studies Computer Science at the Hochschule Furtwangen University located in Germany. The project is taking place in the sixth semester and the group is consisting of four members.
The project is about the implementation of a software for remote camera observation, while a special focus is placed on the interchangeability of the hardware in use. Furthermore, registered users of the product shall be informed automatically when a motion is detected by the software. 
Many providers of similar solutions are using cloud based services to tackle such tasks. By making use of more direct connections between the \acs{IP} camera and the end consumer, this project aims to achieve lower latency.

\vspace{1cm}

Dies ist die Dokumentation zum Semesterprojekt einer vierköpfigen Gruppe aus dem sechsten Semester des Studienganges Allgemeine Informatik der Hochschule in Furtwangen. Bei dem Projekt geht es um die Implementierung einer Software zur Kameraüberwachung, wobei ein besonderer Fokus auf die Austauschbarkeit der Hardware gelegt wird. Zudem sollen durch eine Bewegungserkennung ausgelöste Benachrichtigungen automatisch an registrierte Nutzer versendet werden können. Viele Anbieter ähnlicher Softwarelösungen greifen bei der Umsetzung auf Cloud-Dienste zurück. Durch eine direktere Verbindung zwischen \acs{IP}-Kamera und Endanwender sollen zudem geringere Latenzzeiten als bei zuvor genannten, kommerziellen Produkten erzielt werden.